XOR-Some Prolific Pilot 2

### 2021-05-04 analysis/xor-some-prolific-pilot2.Rmd
add counts of prior response diffs

```
```{r, fig.height=3}
# check whether the ratings in the two prior questions are the same in xor 
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  filter(block == "prior", main_type == "xor") %>%
  mutate(priorQ_nr = rep(c(1,2), 396),
         unique_ID = paste(submission_id, ID, sep="_")) -> d_xor_priors
d_xor_priors %>% group_by(priorQ_nr, prior_class) %>%
  summarise(mean = mean(response)) -> d_xor_priors_summary

d_xor_priors %>%
  ggplot(., aes(x = as.factor(priorQ_nr), y = response )) +
  geom_point(size = 2, alpha = 0.6, position = position_jitter(width = 0.1)) +
  geom_point(data = d_xor_priors_summary, aes(x = as.factor(priorQ_nr), y = mean), color = "red", size = 3) +
  geom_path(aes(group = "unique_ID"), alpha = 0.6) +
  ylab("Responses to prior questions") +
  xlab("First vs Second prior question for high vs low prior conditions") +
  facet_wrap(~as.factor(prior_class)) + # get ratings from the respective trials only 
  ggtitle("Xor prior question ratings.\nLines indicate the two responses provided by one participant for a specific item.")
```

>>>>

```{r, fig.height=3}
# check whether the ratings in the two prior questions are the same in xor 
d_critical_long %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  filter(block == "prior", main_type == "xor") %>%
  mutate(priorQ_nr = rep(c(1,2), 396),
         unique_ID = paste(submission_id, ID, sep="_")) -> d_xor_priors
d_xor_priors %>% group_by(priorQ_nr, prior_class) %>%
  summarise(mean = mean(response)) -> d_xor_priors_summary

d_xor_priors %>%
  ggplot(., aes(x = as.factor(priorQ_nr), y = response )) +
  geom_point(size = 2, alpha = 0.6, position = position_jitter(width = 0.1)) +
  geom_point(data = d_xor_priors_summary, aes(x = as.factor(priorQ_nr), y = mean), color = "red", size = 3) +
  geom_path(aes(group = "unique_ID"), alpha = 0.6) +
  ylab("Responses to prior questions") +
  xlab("First vs Second prior question for high vs low prior conditions") +
  facet_wrap(~as.factor(prior_class)) + # get ratings from the respective trials only 
  ggtitle("Xor prior question ratings.\nLines indicate the two responses provided by one participant for a specific item.")
```
```{r}
# check analytically how many subjects rate prior questions differently
d_xor_priors %>% select(-trial_number, -RT, -prompt) %>% 
  pivot_wider(names_from = "priorQ_nr", values_from = "response") %>%
  mutate(response_difference = abs(`1` - `2`),
         bigDifference = ifelse(response_difference > 15, T, F)) -> d_xor_priors_differences

# 41 responses with difference > 15 between first and second rating
d_xor_priors_differences %>% count(bigDifference)

# proportion of big differences in prior responses by prior type (high vs low)
d_xor_priors_differences %>% group_by(prior_class) %>% summarise(prop_big_diffs = mean(bigDifference))
```
